---
title: "Global sections"
author: "Jens Daniel Müller and Donghe Zhu"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```

# Data sources

Following Cant mean values per grid cell are used:

## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_file}

cant_JDM <-
  read_csv(paste(path_version_data,
                 "cant_3d.csv",
                 sep = ""))

cant_sd <- cant_JDM %>%
  select(lon, 
         lat,
         depth,
         basin,
         basin_AIP,
         eras,
         cant_sd,
         cant_pos_sd,
         gamma,
         gamma_slab)

cant_JDM <- cant_JDM %>%
  select(lon, 
         lat,
         depth,
         basin_AIP,
         eras,
         cant,
         cant_pos)

```

## Model Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_model_cant_file}

cant_M <-
  read_csv(paste(path_version_data,
                  "cant_M.csv", sep = ""))

cant_M <- cant_M %>%
  select(lon, 
         lat,
         depth,
         basin_AIP,
         eras,
         cant,
         cant_pos)

```

## Join data sets

Cant fields are merged, and differences calculate per grid cell and per eras.

```{r join_M_and_JDM_zonal_sections}

# add estimate label
cant_long <- bind_rows(cant_JDM %>%  mutate(estimate = "JDM"),
                             cant_M %>%  mutate(estimate = "M"))

# pivot to wide format
cant_wide <- cant_long %>%
  pivot_wider(names_from = estimate, values_from = cant:cant_pos) %>%
  drop_na()

# calculate offset
cant_wide <- cant_wide %>%
  mutate(
    cant_pos_offset = cant_pos_JDM - cant_pos_M,
    cant_offset = cant_JDM - cant_M,
    estimate = "JDM - M"
  )

# join with SD deviation of Cant across all (currently 10) MLR models for each grid cell
cant_wide <- left_join(cant_wide, cant_sd)

```


# Global sections

## Cant - positive only

```{r cant_pos_global_section, fig.asp=0.6}

for (i_eras in unique(cant_long$eras)) {
  for (i_estimate in unique(cant_long$estimate)) {
   # i_eras = "1982-1999 --> 2000-2012"
   # i_estimate = "JDM"
    print(
      p_section_global(
        df = cant_long %>% filter(estimate == i_estimate, eras == i_eras),
        var = "cant_pos",
        subtitle_text = paste("Estimate:", i_estimate, " | Eras:", i_eras)
      )
    )
    
  }
  print(
    p_section_global(
      df = cant_wide %>% filter(eras == i_eras),
      var = "cant_pos_offset",
      col = "divergent",
      subtitle_text = paste("Estimate: JDM - M | Eras:", i_eras)
    )
  )
}

```

## Cant - all

```{r cant_all_global_section, fig.asp=0.6}

for (i_eras in unique(cant_long$eras)) {
  for (i_estimate in unique(cant_long$estimate)) {
    print(
      p_section_global(
        df = cant_long %>% filter(estimate == i_estimate, eras == i_eras),
        var = "cant",
        col = "divergent",
        subtitle_text = paste("Estimate:", i_estimate, " | Eras:", i_eras)
      )
    )
    
  }
  print(
    p_section_global(
      df = cant_wide %>% filter(eras == i_eras),
      var = "cant_offset",
      col = "divergent",
      subtitle_text = paste("Estimate: JDM - M | Eras:", i_eras)
    )
  )
}

```


# Model quality check

## Cant - positive only

```{r cant_pos_model_quality_check}

cant_wide %>%
  ggplot(aes(cant_pos_sd, cant_pos_offset)) +
  geom_bin2d(binwidth = 5) +
  scale_fill_viridis_c(option = "magma",
                       direction = -1,
                       trans = "log10") +
  facet_grid(eras ~ basin_AIP) +
  labs(title = "The offset vs sd of positive Cant across models")

```

## Cant - all

```{r cant_model_quality_check}

cant_wide %>%
  ggplot(aes(cant_sd, cant_offset)) +
  geom_bin2d(binwidth = 5) +
  scale_fill_viridis_c(option = "magma",
                       direction = -1,
                       trans = "log10") +
  facet_grid(eras ~ basin_AIP) +
  labs(title = "The offset vs sd of Cant across models")

```

