---
title: "Analysis of cant budgets"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```

# Data sources

Following Cant estimates are used:

- Zonal mean for this study and model truth (basin, lat, lon, eras)


## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_zonal_file}

cant_zonal_JDM <-
  read_csv(paste(path_version_data,
                 "cant_zonal.csv",
                 sep = ""))

cant_zonal_JDM <- cant_zonal_JDM %>%
  select(lat,
         depth,
         eras,
         basin_AIP,
         gamma_mean,
         cant_mean,
         cant_pos_mean,
         cant_sd,
         cant_pos_sd)

```

## Modeled Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_modeled_cant_files}
               
tref  <-
  read_csv(paste(path_version_data,
                 "tref.csv",
                 sep = ""))

cant_tref_1 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[1]),
    ".csv",
    sep = ""
  ))

cant_tref_1 <- cant_tref_1 %>%
  rename(cant_tref_1 = cant_total) %>%
  select(-year)

cant_tref_2 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[2]),
    ".csv",
    sep = ""
  ))

cant_tref_2 <- cant_tref_2 %>%
  rename(cant_tref_2 = cant_total) %>%
  select(-year)

cant_tref_3 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[3]),
    ".csv",
    sep = ""
  ))

cant_tref_3 <- cant_tref_3 %>%
  rename(cant_tref_3 = cant_total) %>%
  select(-year)

```

```{r calc_modeled_cant_between_tref}

cant_M_1 <- left_join(cant_tref_1, cant_tref_2) %>%
  mutate(cant = cant_tref_2 - cant_tref_1,
         eras = unique(cant_inv_JDM$eras)[1]) %>% 
  select(-c(cant_tref_1, cant_tref_2))

cant_M_1 <- cant_M_1 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M_2 <- left_join(cant_tref_2, cant_tref_3) %>%
  mutate(cant = cant_tref_3 - cant_tref_2,
         eras = unique(cant_inv_JDM$eras)[2]) %>% 
  select(-c(cant_tref_2, cant_tref_3))

cant_M_2 <- cant_M_2 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M <- full_join(cant_M_1, cant_M_2) %>%
  arrange(lon, lat, depth, basin_AIP)

rm(cant_tref_1, cant_tref_2, cant_tref_3, cant_M_1, cant_M_2)

```

```{r calc_zonal_mean_modeled_cant}

cant_zonal_M <- m_zonal_mean_section(cant_M)

cant_zonal_JDM_gamma <- cant_zonal_JDM %>%
  select(lat, depth, eras, basin_AIP, gamma_mean)

cant_zonal_M <- left_join(cant_zonal_JDM_gamma, cant_zonal_M)

rm(cant_zonal_JDM_gamma)

```

## Join data sets

Zonal sections are merged, and differences calculate per grid cell and per eras.

```{r join_M_and_JDM_zonal_sections}

# add estimate label
cant_zonal_long <- bind_rows(
  cant_zonal_JDM %>%  mutate(estimate = "JDM"),
  cant_zonal_M %>%  mutate(estimate = "M")
  )

# pivot to wide format
cant_zonal_wide <- cant_zonal_long %>% 
  pivot_wider(names_from = estimate, values_from = cant_mean:cant_pos_sd) %>% 
  drop_na()

# calculate offset
cant_zonal_wide <- cant_zonal_wide %>% 
  mutate(cant_pos_mean_offset = cant_pos_mean_JDM - cant_pos_mean_M,
         cant_mean_offset = cant_mean_JDM - cant_mean_M,
         estimate = "JDM - M")

```


# Zonal mean sections

## Cant - positive only

In a first series of plots we explore the distribution of Cant, taking only positive estimates into account (positive here refers to the mean cant estimate across MLR model predictions available for each grid cell). Negative values were set to zero before calculating mean sections and inventories.

### Absolute values

```{r cant_pos_zonal_mean_section, fig.asp=0.6}

for (i_basin_AIP in unique(cant_zonal_long$basin_AIP)) {
  for (i_estimate in unique(cant_zonal_long$estimate)) {
    for (i_eras in unique(cant_zonal_long$eras)) {
      
      print(
        p_section_zonal(
          df = cant_zonal_long %>%
            filter(basin_AIP == i_basin_AIP,
                   estimate == i_estimate,
                   eras == i_eras),
          var = "cant_pos_mean",
          subtitle_text =
            paste("Basin:", i_basin_AIP, "| estimate:", i_estimate, " | Eras:", i_eras)
        )
      )
      
    }
  }
}

```

### Offset

```{r cant_pos_offset_zonal_section, fig.asp=0.6}

for (i_basin_AIP in unique(cant_zonal_wide$basin_AIP)) {
  for (i_eras in unique(cant_zonal_wide$eras)) {
    
    print(
      p_section_zonal(
        df = cant_zonal_wide %>%
          filter(basin_AIP == i_basin_AIP,
                 eras == i_eras),
        var = "cant_pos_mean_offset",
        breaks = params_global$breaks_cant_offset,
        col = "divergent",
        subtitle_text =
          paste("Basin:", i_basin_AIP, "| estimate: JDM-M | Eras:", i_eras)
      )
    )
  }
}

```

## Cant - all

In a second series of plots we explore the distribution of all Cant, taking positive and negative estimates into account.

### Absolute values

```{r cant_zonal_mean_section, fig.asp=0.6}

for (i_basin_AIP in unique(cant_zonal_long$basin_AIP)) {
  for (i_estimate in unique(cant_zonal_long$estimate)) {
    for (i_eras in unique(cant_zonal_long$eras)) {
      
      print(
        p_section_zonal(
          df = cant_zonal_long %>%
            filter(
              basin_AIP == i_basin_AIP,
              estimate == i_estimate,
              eras == i_eras
            ),
          var = "cant_mean",
          col = "divergent",
          breaks = params_global$breaks_cant,
          legend_title = expression(atop(Delta * C[ant],
                                         (mu * mol ~ kg ^ {
                                           -1
                                         }))),
          subtitle_text =
            paste(
              "Basin:",
              i_basin_AIP,
              "| estimate:",
              i_estimate,
              " | Eras:",
              i_eras
            )
        )
        
      )
      
    }
  }
}

```

### Offset

```{r cant_offset_zonal_mean_section, fig.asp=0.6}

for (i_basin_AIP in unique(cant_zonal_wide$basin_AIP)) {
  for (i_eras in unique(cant_zonal_wide$eras)) {
    
    print(
      p_section_zonal(
        df = cant_zonal_wide %>%
          filter(basin_AIP == i_basin_AIP,
                 eras == i_eras),
        var = "cant_mean_offset",
        col = "divergent",
        breaks = params_global$breaks_cant_offset,
        subtitle_text =
          paste("Basin:", i_basin_AIP, "| estimate: JDM - M | eras:", i_eras)
      )
      
    )
  }
}

```

