---
title: "Zonal mean sections"
author: "Jens Daniel Müller and Donghe Zhu"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```

# Data sources

Following Cant zonal mean sections are used:

## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_zonal_file}

cant_zonal_JDM <-
  read_csv(paste(path_version_data,
                 "cant_zonal.csv",
                 sep = ""))

cant_zonal_JDM <- cant_zonal_JDM %>%
  select(lat,
         depth,
         eras,
         basin_AIP,
         gamma_mean,
         cant_mean,
         cant_pos_mean,
         cant_sd,
         cant_pos_sd)

```

## Model Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_model_cant_zonal_file}

cant_zonal_M <-
  read_csv(paste(path_version_data,
                  "cant_zonal_M", sep = ""))

```

```{r assign_gamma_from_JDM_to_model_cant_zonal}

cant_zonal_JDM_gamma <- cant_zonal_JDM %>%
  select(lat, depth, eras, basin_AIP, gamma_mean)

cant_zonal_M <- left_join(cant_zonal_JDM_gamma, cant_zonal_M)

rm(cant_zonal_JDM_gamma)

```

## Join data sets

Zonal sections are merged, and differences calculate per grid cell and per eras.

```{r join_M_and_JDM_zonal_sections}

# add estimate label
cant_zonal_long <- bind_rows(cant_zonal_JDM %>%  mutate(estimate = "JDM"),
                             cant_zonal_M %>%  mutate(estimate = "M"))

# pivot to wide format
cant_zonal_wide <- cant_zonal_long %>%
  pivot_wider(names_from = estimate, values_from = cant_mean:cant_pos_sd) %>%
  drop_na()

# calculate offset
cant_zonal_wide <- cant_zonal_wide %>%
  mutate(
    cant_pos_mean_offset = cant_pos_mean_JDM - cant_pos_mean_M,
    cant_mean_offset = cant_mean_JDM - cant_mean_M,
    estimate = "JDM - M"
  )

```


# Zonal mean sections

## Cant - positive only

In a first series of plots we explore the distribution of Cant, taking only positive estimates into account (positive here refers to the mean cant estimate across MLR model predictions available for each grid cell). Negative values were set to zero before calculating mean sections.

```{r cant_pos_zonal_mean_section, fig.asp=0.6}

for (i_eras in unique(cant_zonal_long$eras)) {
  for (i_basin_AIP in unique(cant_zonal_long$basin_AIP)) {
    for (i_estimate in unique(cant_zonal_long$estimate)) {
      # Absolute values
      print(
        p_section_zonal(
          df = cant_zonal_long %>%
            filter(
              basin_AIP == i_basin_AIP,
              estimate == i_estimate,
              eras == i_eras
            ),
          var = "cant_pos_mean",
          subtitle_text =
            paste(
              "Basin:",
              i_basin_AIP,
              "| estimate:",
              i_estimate,
              " | eras:",
              i_eras
            )
        )
      )
      
    }
    
    # Offset
    print(
      p_section_zonal(
        df = cant_zonal_wide %>%
          filter(basin_AIP == i_basin_AIP,
                 eras == i_eras),
        var = "cant_pos_mean_offset",
        breaks = params_global$breaks_cant_offset,
        col = "divergent",
        title_text = "Zonal mean section - offset",
        subtitle_text =
          paste("Basin:", i_basin_AIP, "| estimate: JDM-M | eras:", i_eras)
      )
    )
  }
}

```

## Cant - all

In a second series of plots we explore the distribution of all Cant, taking positive and negative estimates into account.


```{r cant_zonal_mean_section, fig.asp=0.6}

for (i_eras in unique(cant_zonal_long$eras)) {
  for (i_basin_AIP in unique(cant_zonal_long$basin_AIP)) {
    for (i_estimate in unique(cant_zonal_long$estimate)) {
      # Absolute values
      print(
        p_section_zonal(
          df = cant_zonal_long %>%
            filter(
              basin_AIP == i_basin_AIP,
              estimate == i_estimate,
              eras == i_eras
            ),
          var = "cant_mean",
          col = "divergent",
          breaks = params_global$breaks_cant,
          legend_title = expression(atop(Delta * C[ant],
                                         (mu * mol ~ kg ^ {
                                           -1
                                         }))),
          subtitle_text =
            paste(
              "Basin:",
              i_basin_AIP,
              "| estimate:",
              i_estimate,
              " | eras:",
              i_eras
            )
        )
        
      )
      
    }
    
    # Offset
    print(
      p_section_zonal(
        df = cant_zonal_wide %>%
          filter(basin_AIP == i_basin_AIP,
                 eras == i_eras),
        var = "cant_mean_offset",
        col = "divergent",
        breaks = params_global$breaks_cant_offset,
        title_text = "Zonal mean section - offset",
        subtitle_text =
          paste("Basin:", i_basin_AIP, "| estimate: JDM - M | eras:", i_eras)
      )
      
    )
  }
}

```
