---
title: "Isoneutral slab distribution"
author: "Jens Daniel Müller and Donghe Zhu"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```

# Data sources

Following Cant mean values per grid cell are used:

## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_file}

cant_3d <-
  read_csv(paste(path_version_data,
                 "cant_3d.csv",
                 sep = ""))

```

## Model Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_model_cant_file}

cant_M <-
  read_csv(paste(path_version_data,
                  "cant_M.csv", sep = ""))

```

```{r assign_gamma_from_JDM_to_model_cant}

cant_3d_gamma <- cant_3d %>%
  select(lon, lat, depth, eras, basin_AIP, gamma, gamma_slab)

cant_M <- left_join(cant_3d_gamma, cant_M)

rm(cant_3d_gamma)

```


# Isoneutral slab distribution

Cant mean within each horizontal grid cell (lon x lat) per isoneutral slab.

Please note that:

- density slabs covering values >28.1 occur by definition only either in the Atlantic or Indo-Pacific basin
- gaps in the maps represent areas where (thin) density layers fit between discrete depth levels used for mapping

```{r calc_gamma_slab_maps}

# JDM
cant_gamma_maps_JDM <- m_cant_slab(cant_3d)

cant_gamma_maps_JDM <- cant_gamma_maps_JDM %>%
  arrange(gamma_slab, eras)

# M
cant_gamma_maps_M <- m_cant_slab(cant_M)

cant_gamma_maps_M <- cant_gamma_maps_M %>%
  arrange(gamma_slab, eras)

```


## Join data sets

Gamma slab maps are merged, and differences calculate per grid cell and per eras.

```{r join_M_and_JDM_gamma_slab_maps}

# add estimate label
cant_gamma_maps_long <- bind_rows(cant_gamma_maps_JDM %>%  mutate(estimate = "JDM"),
                           cant_gamma_maps_M %>%  mutate(estimate = "M"))

# pivot to wide format
cant_gamma_maps_wide <- cant_gamma_maps_long %>%
  pivot_wider(names_from = estimate, values_from = cant_pos:cant) %>%
  drop_na()

# calculate offset
cant_gamma_maps_wide <- cant_gamma_maps_wide %>%
  mutate(
    cant_pos_offset = cant_pos_JDM - cant_pos_M,
    cant_offset = cant_JDM - cant_M,
    estimate = "JDM - M"
  )

```


## Cant - positive

In a first series of plots we explore the distribution of Cant, taking only positive estimates into account (positive here refers to the mean cant estimate across MLR model predictions available for each grid cell). Negative values were set to zero before calculating slab inventories.

```{r cant_pos_gamma_slab_maps, fig.asp=0.5}


for (i_eras in unique(cant_gamma_maps_long$eras)) {
  for (i_gamma_slab in unique(cant_gamma_maps_long$gamma_slab)) {
    for (i_estimate in unique(cant_gamma_maps_long$estimate)) {
      print(p_map_cant_slab(
        df = cant_gamma_maps_long %>%
          filter(
            estimate == i_estimate,
            eras == i_eras,
            gamma_slab == i_gamma_slab
          ),
        subtitle_text = paste(
          "Estimate:",
          i_estimate,
          "Eras:",
          i_eras,
          "| Neutral density:",
          i_gamma_slab
        )
      ))
      
    }
    print(
      p_map_cant_slab(
        df = cant_gamma_maps_wide %>%
          filter(
            eras == i_eras,
            gamma_slab == i_gamma_slab
          ),
        var = "cant_pos_offset",
        col = "divergent",
        subtitle_text = paste(
          "Estimate: JDM - M | Eras:",
          i_eras,
          "| Neutral density:",
          i_gamma_slab
        )
      )
    )
  }
}

```

## Cant - all

In a second series of plots we explore the distribution of all Cant, taking positive and negative estimates into account.

```{r cant_all_gamma_slab_maps, fig.asp=0.5}

for (i_eras in unique(cant_gamma_maps_long$eras)) {
  for (i_gamma_slab in unique(cant_gamma_maps_long$gamma_slab)) {
    for (i_estimate in unique(cant_gamma_maps_long$estimate)) {
      print(
        p_map_cant_slab(
          df = cant_gamma_maps_long %>%
            filter(
              estimate == i_estimate,
              eras == i_eras,
              gamma_slab == i_gamma_slab
            ),
          var = "cant",
          col = "divergent",
          subtitle_text = paste(
            "Estimate:",
            i_estimate,
            "Eras:",
            i_eras,
            "| Neutral density:",
            i_gamma_slab
          )
        )
      )
      
    }
    print(
      p_map_cant_slab(
        df = cant_gamma_maps_wide %>%
          filter(
            eras == i_eras,
            gamma_slab == i_gamma_slab
          ),
        var = "cant_offset",
        col = "divergent",
        subtitle_text = paste(
          "Estimate: JDM - M | Eras:",
          i_eras,
          "| Neutral density:",
          i_gamma_slab
        )
      )
    )
  }
}

```
