---
title: "Cant budgets"
author: "Jens Daniel Müller and Donghe Zhu"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```


# Data sources

Following Cant column inventories are used:

## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_inv_file}

cant_inv_JDM <-
  read_csv(paste(path_version_data,
                 "cant_inv.csv",
                 sep = ""))

```

## Model Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_model_cant_inv_file}

cant_inv_M <-
  read_csv(paste(path_version_data,
                  "cant_inv_M.csv", sep = ""))

```

## Join data sets

Inventories are merged, and differences calculate per grid cell and per eras.

```{r join_M_and_JDM_inventories}

# add estimate label
cant_inv_long <- bind_rows(cant_inv_JDM %>%  mutate(estimate = "JDM"),
                           cant_inv_M %>%  mutate(estimate = "M"))

# pivot to wide format
cant_inv_wide <- cant_inv_long %>%
  pivot_wider(names_from = estimate, values_from = cant_pos_inv:cant_inv)

# calculate offset
cant_inv_wide <- cant_inv_wide %>%
  mutate(
    cant_pos_inv_offset = cant_pos_inv_JDM - cant_pos_inv_M,
    cant_inv_offset = cant_inv_JDM - cant_inv_M
  )

```

# Cant budgets

Global Cant inventories budget were estimated separately for ocean basins in units of Pg C, based on all vs positive only Cant estimates. 

Results were integrated over the upper `r params_global$inventory_depths` m of the water column.

```{r calculate_global_inventory}

# calculate budgets
cant_inv_budget <- cant_inv_wide %>%
  mutate(
    surface_area = earth_surf(lat, lon),
    cant_inv_grid_JDM = cant_inv_JDM * surface_area,
    cant_inv_grid_M = cant_inv_M * surface_area,
    cant_pos_inv_grid_JDM = cant_pos_inv_JDM * surface_area,
    cant_pos_inv_grid_M = cant_pos_inv_M * surface_area,
    cant_inv_offset_grid = cant_inv_offset * surface_area,
    cant_pos_inv_offset_grid = cant_pos_inv_offset * surface_area
  ) %>%
  group_by(basin_AIP, eras, inv_depth) %>%
  summarise(
    cant_JDM = sum(cant_inv_grid_JDM) * 12 * 1e-15,
    cant_JDM = round(cant_JDM, 1),
    cant_M = sum(cant_inv_grid_M) * 12 * 1e-15,
    cant_M = round(cant_M, 1),
    cant_pos_JDM = sum(cant_pos_inv_grid_JDM) * 12 * 1e-15,
    cant_pos_JDM = round(cant_pos_JDM, 1),
    cant_pos_M = sum(cant_pos_inv_grid_M) * 12 * 1e-15,
    cant_pos_M = round(cant_pos_M, 1),
    cant_inv_offset = sum(cant_inv_offset_grid) * 12 * 1e-15,
    cant_inv_offset = round(cant_inv_offset, 1),
    cant_pos_inv_offset = sum(cant_pos_inv_offset_grid) * 12 * 1e-15,
    cant_pos_inv_offset = round(cant_pos_inv_offset, 1)
  ) %>%
  ungroup()

# print budget table
cant_inv_budget %>%
  gt(
    rowname_col = "basin_AIP",
    groupname_col = c("eras", "inv_depth"),
    row_group.sep = " | Depth: "
  ) %>%
  summary_rows(groups = TRUE,
               fns = list(total = "sum"))

rm(cant_inv_budget)

```

