---
title: "Analysis - isoneutral slab"
author: "Jens Daniel Müller and Donghe Zhu"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```

# Data sources

Following Cant estimates are used:

- Mean and SD per grid cell for this study and model truth (basin, lat, lon, eras)


## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_file}

cant_3d <-
  read_csv(paste(path_version_data,
                 "cant_3d.csv",
                 sep = ""))

```

## Modeled Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_model_cant_files}

tref  <-
  read_csv(paste(path_version_data,
                 "tref.csv",
                 sep = ""))

cant_tref_1 <-
  read_csv(
    paste(
      path_preprocessing,
      "cant_annual_field_",
      params_local$model_runs,
      "/cant_",
      unique(tref$year[1]),
      ".csv",
      sep = ""
    )
  )

cant_tref_1 <- cant_tref_1 %>%
  rename(cant_tref_1 = cant_total) %>%
  select(-year)

cant_tref_2 <-
  read_csv(
    paste(
      path_preprocessing,
      "cant_annual_field_",
      params_local$model_runs,
      "/cant_",
      unique(tref$year[2]),
      ".csv",
      sep = ""
    )
  )

cant_tref_2 <- cant_tref_2 %>%
  rename(cant_tref_2 = cant_total) %>%
  select(-year)

cant_tref_3 <-
  read_csv(
    paste(
      path_preprocessing,
      "cant_annual_field_",
      params_local$model_runs,
      "/cant_",
      unique(tref$year[3]),
      ".csv",
      sep = ""
    )
  )

cant_tref_3 <- cant_tref_3 %>%
  rename(cant_tref_3 = cant_total) %>%
  select(-year)

```

```{r calc_model_cant_between_tref}

cant_M_1 <- left_join(cant_tref_1, cant_tref_2) %>%
  mutate(cant = cant_tref_2 - cant_tref_1,
         eras = unique(cant_3d$eras)[1]) %>% 
  select(-c(cant_tref_1, cant_tref_2))

cant_M_1 <- cant_M_1 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M_2 <- left_join(cant_tref_2, cant_tref_3) %>%
  mutate(cant = cant_tref_3 - cant_tref_2,
         eras = unique(cant_3d$eras)[2]) %>% 
  select(-c(cant_tref_2, cant_tref_3))

cant_M_2 <- cant_M_2 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M <- full_join(cant_M_1, cant_M_2) %>%
  arrange(lon, lat, depth, basin_AIP)

rm(cant_tref_1, cant_tref_2, cant_tref_3, cant_M_1, cant_M_2)

```

```{r add_gamma_to_model_cant}

cant_3d_gamma <- cant_3d %>%
  select(lon, lat, depth, eras, basin_AIP, gamma, gamma_slab)

cant_M <- left_join(cant_3d_gamma, cant_M)

rm(cant_3d_gamma)

```

```{r calculate_gamma_slab_maps}

cant_gamma_maps_JDM <- m_cant_slab(cant_3d)

cant_gamma_maps_JDM <- cant_gamma_maps_JDM %>%
  arrange(gamma_slab, eras)

cant_gamma_maps_M <- m_cant_slab(cant_M)

cant_gamma_maps_M <- cant_gamma_maps_M %>%
  arrange(gamma_slab, eras)

```


# Isoneutral slab distribution

Cant mean within each horizontal grid cell (lon x lat) per isoneutral slab.

Please note that:

- density slabs covering values >28.1 occur by definition only either in the Atlantic or Indo-Pacific basin
- gaps in the maps represent areas where (thin) density layers fit between discrete depth levels used for mapping

## Cant - positive

In a first series of plots we explore the distribution of Cant, taking only positive estimates into account (positive here refers to the mean cant estimate across MLR model predictions available for each grid cell). Negative values were set to zero before calculating mean sections and inventories.

```{r cant_pos_gamma_slab_maps, fig.asp=0.5}

for (i_eras in unique(cant_gamma_maps_JDM$eras)) {
  for (i_gamma_slab in unique(cant_gamma_maps_JDM$gamma_slab)) {
    
    print(p_map_cant_slab(
      df = cant_gamma_maps_JDM %>%
        filter(eras == i_eras,
               gamma_slab == i_gamma_slab),
      subtitle_text = paste(
        "Eras:",
        i_eras,
        "| Neutral density:",
        i_gamma_slab,
        "| Estimate: JDM"
      )
    ))
    
  }
}

for (i_eras in unique(cant_gamma_maps_M$eras)) {
  for (i_gamma_slab in unique(cant_gamma_maps_M$gamma_slab)) {
    
    print(p_map_cant_slab(
      df = cant_gamma_maps_M %>%
        filter(eras == i_eras,
               gamma_slab == i_gamma_slab),
      subtitle_text = paste(
        "Eras:",
        i_eras,
        "| Neutral density:",
        i_gamma_slab,
        "| Estimate: M"
      )
    ))
    
  }
}

```

## Cant - all

In a second series of plots we explore the distribution of all Cant, taking positive and negative estimates into account.

```{r cant_all_gamma_slab_maps, fig.asp=0.5}

for (i_eras in unique(cant_gamma_maps_JDM$eras)) {
  for (i_gamma_slab in unique(cant_gamma_maps_JDM$gamma_slab)) {
    
    print(
      p_map_cant_slab(
        df = cant_gamma_maps_JDM %>%
          filter(eras == i_eras,
                 gamma_slab == i_gamma_slab),
        var = "cant",
        col = "divergent",
        subtitle_text = paste(
          "Eras:",
          i_eras,
          "| Neutral density:",
          i_gamma_slab,
          "| Estimate: JDM"
        )
      )
    )
    
  }
}

for (i_eras in unique(cant_gamma_maps_M$eras)) {
  for (i_gamma_slab in unique(cant_gamma_maps_M$gamma_slab)) {
    
    print(
      p_map_cant_slab(
        df = cant_gamma_maps_M %>%
          filter(eras == i_eras,
                 gamma_slab == i_gamma_slab),
        var = "cant",
        col = "divergent",
        subtitle_text = paste(
          "Eras:",
          i_eras,
          "| Neutral density:",
          i_gamma_slab,
          "| Estimate: M"
        )
      )
    )
    
  }
}

```
