---
title: "Analysis - inventory maps"
author: "Jens Daniel Müller and Donghe Zhu"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```

# Data sources

Following Cant estimates are used:

- Inventories for this study and model truth (lat, lon, eras)


## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_inv_file}

cant_inv_JDM <-
  read_csv(paste(path_version_data,
                 "cant_inv.csv",
                 sep = ""))

```

## Modeled Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_modeled_cant_files}

tref  <-
  read_csv(paste(path_version_data,
                 "tref.csv",
                 sep = ""))

cant_tref_1 <-
  read_csv(
    paste(
      path_preprocessing,
      "cant_annual_field_",
      params_local$model_runs,
      "/cant_",
      unique(tref$year[1]),
      ".csv",
      sep = ""
    )
  )

cant_tref_1 <- cant_tref_1 %>%
  rename(cant_tref_1 = cant_total) %>%
  select(-year)

cant_tref_2 <-
  read_csv(
    paste(
      path_preprocessing,
      "cant_annual_field_",
      params_local$model_runs,
      "/cant_",
      unique(tref$year[2]),
      ".csv",
      sep = ""
    )
  )

cant_tref_2 <- cant_tref_2 %>%
  rename(cant_tref_2 = cant_total) %>%
  select(-year)

cant_tref_3 <-
  read_csv(
    paste(
      path_preprocessing,
      "cant_annual_field_",
      params_local$model_runs,
      "/cant_",
      unique(tref$year[3]),
      ".csv",
      sep = ""
    )
  )

cant_tref_3 <- cant_tref_3 %>%
  rename(cant_tref_3 = cant_total) %>%
  select(-year)

```

```{r calc_modeled_cant_between_tref}

cant_M_1 <- left_join(cant_tref_1, cant_tref_2) %>%
  mutate(cant = cant_tref_2 - cant_tref_1,
         eras = unique(cant_inv_JDM$eras)[1]) %>% 
  select(-c(cant_tref_1, cant_tref_2))

cant_M_1 <- cant_M_1 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M_2 <- left_join(cant_tref_2, cant_tref_3) %>%
  mutate(cant = cant_tref_3 - cant_tref_2,
         eras = unique(cant_inv_JDM$eras)[2]) %>% 
  select(-c(cant_tref_2, cant_tref_3))

cant_M_2 <- cant_M_2 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M <- full_join(cant_M_1, cant_M_2) %>%
  arrange(lon, lat, depth, basin_AIP)

rm(cant_tref_1, cant_tref_2, cant_tref_3, cant_M_1, cant_M_2)

```

```{r calculate_inventory_modeled_cant}

cant_inv_M <- m_cant_inv(cant_M)

```

## Join data sets

Inventories are merged, and differences calculate per grid cell and per eras.

```{r join_M_and_JDM_inventories}

# add estimate label
cant_inv_long <- bind_rows(cant_inv_JDM %>%  mutate(estimate = "JDM"),
                           cant_inv_M %>%  mutate(estimate = "M"))

# pivot to wide format
cant_inv_wide <- cant_inv_long %>%
  pivot_wider(names_from = estimate, values_from = cant_pos_inv:cant_inv) %>%
  drop_na()

# calculate offset
cant_inv_wide <- cant_inv_wide %>%
  mutate(
    cant_pos_inv_offset = cant_pos_inv_JDM - cant_pos_inv_M,
    cant_inv_offset = cant_inv_JDM - cant_inv_M
  )

# restrict to the standard inventory depth
cant_inv_long <- cant_inv_long %>%
  filter(inv_depth == params_global$inventory_depth_standard)

cant_inv_wide <- cant_inv_wide %>%
  filter(inv_depth == params_global$inventory_depth_standard)

```


# Inventory maps

This analysis is restricted to the standard inventory depth of `r params_global$inventory_depth_standard` m.

## Cant - positive only

In a first series of plots we explore the distribution of Cant, taking only positive estimates into account (positive here refers to the mean cant estimate across the MLR model predictions available for each grid cell). Negative values were set to zero before calculating mean sections and inventories.

### Absolute values

Column inventory of positive Cant between the surface and `r params_global$inventory_depth_standard`m water depth per horizontal grid cell (lat x lon).

```{r cant_pos_inventory_map, fig.asp=0.5}

for (i_estimate in unique(cant_inv_long$estimate)) {
  for (i_eras in unique(cant_inv_long$eras)) {
    
    print(p_map_cant_inv(
      cant_inv_long %>% filter(estimate == i_estimate, eras == i_eras),
      subtitle_text = paste("Estimate:", i_estimate, " | Eras:", i_eras)
    ))
    
  }
}

```

### Offset

Column inventory offset of positive cant between the surface and `r params_global$inventory_depth_standard`m water depth per horizontal grid cell (lat x lon).

```{r cant_pos_offset_inventory_map, fig.asp=0.5}

for (i_eras in unique(cant_inv_wide$eras)) {
  
  print(
    p_map_cant_inv_offset(
      cant_inv_wide %>% filter(eras == i_eras),
      "cant_pos_inv_offset",
      subtitle_text = paste("Estimate JDM - M | Eras:", i_eras)
    )
  )
  
}

```

## Cant - all

In a second series of plots we explore the distribution of Cant, taking positive and negative estimates into account (positive here refers to the mean cant estimate across MLR model predictions available for each grid cell).

### Absolute values

Column inventory of Cant (including positive and negative values) between the surface and `r params_global$inventory_depth_standard`m water depth per horizontal grid cell (lat x lon).

```{r cant_inventory_map, fig.asp=0.5}

for (i_estimate in unique(cant_inv_long$estimate)) {
  for (i_eras in unique(cant_inv_long$eras)) {
    
    print(
      p_map_cant_inv(
        cant_inv_long %>% filter(estimate == i_estimate, eras == i_eras),
        subtitle_text = paste("Estimate:", i_estimate, " | Eras:", i_eras),
        col = "divergent"
      )
    )
    
  }
}

```

### Offset

Column inventory offset of Cant (including positive and negative values) between the surface and `r params_global$inventory_depth_standard`m water depth per horizontal grid cell (lat x lon).

```{r cant_offset_inventory_map, fig.asp = 0.5}

for (i_eras in unique(cant_inv_wide$eras)) {
  
  print(
    p_map_cant_inv_offset(
      df = cant_inv_wide %>% filter(eras == i_eras),
      var = "cant_inv_offset",
      subtitle_text = paste("Estimate JDM - M | Eras:", i_eras)
    )
  )
  
}

```

