---
title: "Analysis of cant budgets"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```


```{r load_libraries_specific, include = FALSE}
library(scales)
library(marelac)
library(gt)
```


# Data sources

Following Cant estimates are used:

- Inventories for this study and model truth (lat, lon, eras)


## This study

Results from this study are referred to as JDM.

```{r read_JDM_cant_inv_file}

cant_inv_JDM <-
  read_csv(paste(path_version_data,
                 "cant_inv.csv",
                 sep = ""))

```

## Modeled Cant

"True" Cant fields directly inferred from the model output are referred to as M.

```{r read_modeled_cant_files}
               
tref  <-
  read_csv(paste(path_version_data,
                 "tref.csv",
                 sep = ""))

cant_tref_1 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[1]),
    ".csv",
    sep = ""
  ))

cant_tref_1 <- cant_tref_1 %>%
  rename(cant_tref_1 = cant_total) %>%
  select(-year)

cant_tref_2 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[2]),
    ".csv",
    sep = ""
  ))

cant_tref_2 <- cant_tref_2 %>%
  rename(cant_tref_2 = cant_total) %>%
  select(-year)

cant_tref_3 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[3]),
    ".csv",
    sep = ""
  ))

cant_tref_3 <- cant_tref_3 %>%
  rename(cant_tref_3 = cant_total) %>%
  select(-year)

```

```{r calc_modeled_cant_between_tref}

cant_M_1 <- left_join(cant_tref_1, cant_tref_2) %>%
  mutate(cant = cant_tref_2 - cant_tref_1,
         eras = unique(cant_inv_JDM$eras)[1]) %>% 
  select(-c(cant_tref_1, cant_tref_2))

cant_M_1 <- cant_M_1 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M_2 <- left_join(cant_tref_2, cant_tref_3) %>%
  mutate(cant = cant_tref_3 - cant_tref_2,
         eras = unique(cant_inv_JDM$eras)[2]) %>% 
  select(-c(cant_tref_2, cant_tref_3))

cant_M_2 <- cant_M_2 %>% 
   mutate(cant_pos = if_else(cant <= 0, 0, cant))

cant_M <- full_join(cant_M_1, cant_M_2) %>%
  arrange(lon, lat, depth, basin_AIP)

rm(cant_tref_1, cant_tref_2, cant_tref_3, cant_M_1, cant_M_2)

```

```{r calculate_inventory_modeled_cant}

cant_inv_M <- m_cant_inv(cant_M)

```

## Join data sets

Inventories are merged, and differences calculate per grid cell and per eras.

```{r join_M_and_JDM_inventories}

# add estimate label
cant_inv_long <- bind_rows(
  cant_inv_JDM %>%  mutate(estimate = "JDM"),
  cant_inv_M %>%  mutate(estimate = "M")
  )

# pivot to wide format
cant_inv_wide <- cant_inv_long %>% 
  pivot_wider(names_from = estimate, values_from = cant_pos_inv:cant_inv) %>% 
  drop_na()

# calculate offset
cant_inv_wide <- cant_inv_wide %>% 
  mutate(cant_pos_inv_offset = cant_pos_inv_JDM - cant_pos_inv_M,
         cant_inv_offset = cant_inv_JDM - cant_inv_M)

```

# Cant budgets

Global Cant inventories budget were estimated for different ocean basins in units of Pg C, based on all vs positive only Cant estimates. 
Results integrated over the upper `r params_global$inventory_depths` m

```{r calculate_global_inventory}

# calculate budgets
cant_inv_budget <- cant_inv_wide %>% 
  mutate(surface_area = earth_surf(lat, lon),
         cant_inv_grid_JDM = cant_inv_JDM*surface_area,
         cant_inv_grid_M = cant_inv_M*surface_area,
         cant_pos_inv_grid_JDM = cant_pos_inv_JDM*surface_area,
         cant_pos_inv_grid_M = cant_pos_inv_M*surface_area,
         cant_inv_offset_grid = cant_inv_offset*surface_area,
         cant_pos_inv_offset_grid = cant_pos_inv_offset*surface_area) %>% 
  group_by(basin_AIP, eras, inv_depth) %>% 
  summarise(cant_total_JDM = sum(cant_inv_grid_JDM)*12*1e-15,
            cant_total_JDM = round(cant_total_JDM,1),
            cant_total_M = sum(cant_inv_grid_M)*12*1e-15,
            cant_total_M = round(cant_total_M,1),
            cant_pos_total_JDM = sum(cant_pos_inv_grid_JDM)*12*1e-15,
            cant_pos_total_JDM = round(cant_pos_total_JDM,1),
            cant_pos_total_M = sum(cant_pos_inv_grid_M)*12*1e-15,
            cant_pos_total_M = round(cant_pos_total_M,1),
            cant_inv_offset = sum(cant_inv_offset_grid)*12*1e-15,
            cant_inv_offset = round(cant_inv_offset,1),
            cant_pos_inv_offset = sum(cant_pos_inv_offset_grid)*12*1e-15,
            cant_pos_inv_offset = round(cant_pos_inv_offset,1)) %>% 
  ungroup()

# print budget table
cant_inv_budget %>%
  gt(rowname_col = "basin_AIP",
     groupname_col = c("eras", "inv_depth"),
     row_group.sep = " | Depth: ") %>%
  summary_rows(
    groups = TRUE,
    fns = list(total = "sum")
  )

rm(cant_inv_budget)

```

