---
title: "eMLR - data preparation"
author: "Jens Daniel Müller and Donghe Zhu"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r read_params_local, include = FALSE}
params_local <-
  read_rds(here::here("data/auxillary",
                       "params_local.rds"))

```

```{r define_paths, include = FALSE}

path_model <-
  paste(path_root, "/model/", sep = "")

path_preprocessing    <-
  paste(path_model, "preprocessing/", sep = "")

path_version_data     <-
  paste(path_model,
        params_local$Version_ID,
        "/data/",
        sep = "")

path_version_figures  <-
  paste(path_model,
        params_local$Version_ID,
        "/figures/",
        sep = "")
```

```{r load_libraries_specific, include = FALSE}
library(marelac)
library(lubridate)
library(knitr)
library(kableExtra)
```

# Required data

Required are: 

- Synthetic cmorized model subsetting data based on preprocessed GLODAP data
  - cleaned data file
- Cmorized annual cant field for three reference year
- Cmorized annual mean atmospheric pCO~2~ 

```{r read_subsetting_data_sets}

if (params_local$subsetting == "GLODAP") {
  
GLODAP <-
  read_csv(paste(
    path_version_data,
    "GLODAPv2.2020_clean_GLODAP.csv",
    sep = ""
  ))

}

if (params_local$subsetting == "random") {
  
GLODAP <-
  read_csv(paste(
    path_version_data,
    "GLODAPv2.2020_clean_random.csv",
    sep = ""
  ))

}

```

# Calculation of tref

Calculate the reference year for each era and store it as csv file for further selection of corresponding Cant fields.

```{r calc_tref}

# calculate reference year
tref <- GLODAP %>%
  group_by(era) %>%
  summarise(year = round(median(year))) %>%
  ungroup()

# write file
tref  %>%  write_csv(paste(path_version_data,
                           "tref.csv",
                           sep = ""))

```

```{r read_tref_and_pco2_files}

cant_tref_1 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[1]),
    ".csv",
    sep = ""
  ))

cant_tref_2 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[2]),
    ".csv",
    sep = ""
  ))

cant_tref_3 <-
  read_csv(paste(
    path_preprocessing,
    "cant_annual_field_", params_local$model_runs, "/cant_",
    unique(tref$year[3]),
    ".csv",
    sep = ""
  ))

co2_atm <-
  read_csv(paste(path_preprocessing,
                 "co2_atm.csv",
                 sep = ""))

```


# PO~4~*

## Calculation 

The predictor PO~4~* was be calculated according to Clement and Gruber (2018), ie based on oxygen. Please note that an erroneous equations for PO4* calculation is given in the supplement of Gruber et al (2019), based on nitrate.  

Here we use following equation:

```{r calculate_phosphate_star}

print(b_phosphate_star)

if ("phosphate_star" %in% params_local$MLR_predictors) {
GLODAP <- GLODAP %>% 
  mutate(phosphate_star = b_phosphate_star(phosphate, oxygen))
}

```


# C*

C* serves as a conservative tracer of anthropogenic CO~2~ uptake. It is derived from synthetic subsetted DIC by removing the impact of  

- organic matter formation and respiration
- calcification and calcium carbonate dissolution

Contributions of those processes are estimated from phosphate and alkalinity concentrations.

## Stoichiometric ratios

The stoichiometric nutrient ratios for the production and mineralization of organic matter were set to:

- C/P: `r params_local$rCP`
- N/P: `r params_local$rNP`

## Calculation

C* was calculated as:  

```{r calculate_cstar}

print(b_cstar)

GLODAP <- GLODAP %>% 
  mutate(rCP_phosphate = -params_local$rCP * phosphate,
         talk_05 = -0.5 * talk,
         rNP_phosphate_05 = -0.5 * params_local$rNP * phosphate,
         cstar = b_cstar(tco2, phosphate, talk))

```

## Reference year adjustment

To adjust C* values to the reference year of each observation period, we assume a transient steady state change of cant between the time of model subsetting and the reference year. The adjustment requires an approximation of the cant concentration at the reference year. We here use the model-estimated annual cant field for each reference year.


### Cant at tref

Read in Cant field for each reference year.

```{r calculate_cant_tref}

# print reference year table
kable(tref) %>%
  add_header_above() %>%
  kable_styling()

# join cant with tref
cant_3d <- bind_rows(cant_tref_1, cant_tref_2, cant_tref_3)

cant_3d <- left_join(cant_3d, tref) %>%
  arrange(lon, lat, depth) %>% 
  select(lon, lat, depth, era, cant_total)

rm(cant_tref_1, cant_tref_2, cant_tref_3)

```


```{r cant_surface_maps}

map +
  geom_raster(data = cant_3d %>% filter(depth == 5),
              aes(lon, lat, fill = cant_total)) +
  facet_wrap(~ era, ncol = 1) +
  scale_fill_viridis_c() +
  labs(title = "Surface total Cant concentration")

```


### Combine GLODAP + Cant

```{r merge_cstar_cant, fig.asp=1}

# observations grid per era
GLODAP_obs_grid_era <- GLODAP %>% 
  distinct(lat, lon, era)

# cant data at observations grid
cant_3d_obs <- left_join(
  GLODAP_obs_grid_era,
  cant_3d)

# calculate number of cant data points per grid cell
cant_3d_obs <- cant_3d_obs %>%
  group_by(lon, lat, era) %>% 
  mutate(n = n()) %>% 
  ungroup()

# GLODAP-based model subset with only one Cant value
map +
  geom_bin2d(data = cant_3d_obs,
             aes(lon, lat),
             binwidth = 1) +
  scale_fill_viridis_c() +
  facet_wrap(~ era, ncol = 1) +
  labs(title = "Number of Cant depth levels",
       subtitle = "available per latxlon grid cell")

rm(cant_3d, GLODAP_obs_grid_era)

GLODAP_cant_obs <- full_join(GLODAP, cant_3d_obs)

rm(GLODAP, cant_3d_obs)

# fill number of cant data points per grid cell to all model subsetting
GLODAP_cant_obs <- GLODAP_cant_obs %>%
  group_by(lon, lat, era) %>% 
  fill(n, .direction = "updown") %>% 
  ungroup()

```

The model-estimated annual cant fields were merged with GLODAP-based synthetic cmorized model subsetting by:

- using an identical 1x1° horizontal grid
- linear interpolation of C~ant~ from standard to subsetting depth

```{r cant_interpolation_to_observations}

# define positive cant values
GLODAP_cant_obs <- GLODAP_cant_obs %>%
  mutate(cant_total_pos = if_else(cant_total < 0, 0, cant_total))

# interpolate cant to subsetting depth
GLODAP_cant_obs_int <- GLODAP_cant_obs %>%
  filter(n > 1) %>% 
  group_by(lat, lon, era) %>%
  arrange(depth) %>%
  mutate(cant_int = approxfun(depth, cant_total_pos, rule = 2)(depth)) %>%
  ungroup()

# set cant for subsetting depth if only one cant available
#GLODAP_cant_obs_set <- GLODAP_cant_obs %>%
#  filter(n == 1) %>%
#  group_by(lat, lon, era) %>%
#  mutate(cant_int = mean(cant_total, na.rm = TRUE)) %>%
#  ungroup()

### bin data sets with interpolated and set cant
GLODAP_cant_obs <- GLODAP_cant_obs_int
rm(GLODAP_cant_obs_int)

if (params_local$subsetting == "GLODAP") {
  ggplot() +
    geom_path(
      data = GLODAP_cant_obs %>%
        filter(lat == 48.5, lon == 165.5, !is.na(cant_total)) %>%
        arrange(depth),
      aes(cant_total, depth, col = "mapped")
    ) +
    geom_point(
      data = GLODAP_cant_obs %>%
        filter(lat == 48.5, lon == 165.5, !is.na(cant_total)) %>%
        arrange(depth),
      aes(cant_total, depth, col = "mapped")
    ) +
    geom_point(
      data = GLODAP_cant_obs %>%
        filter(lat == 48.5, lon == 165.5, date == ymd("2018-06-27")),
      aes(cant_int, depth, col = "interpolated")
    ) +
    scale_y_reverse() +
    facet_wrap( ~ era) +
    scale_color_brewer(palette = "Dark2", name = "") +
    labs(title = "Cant interpolation to subsetting depth - example profile")
  
}

if (params_local$subsetting == "random") {
  ggplot() +
    geom_path(
      data = GLODAP_cant_obs %>%
        filter(lat == 48.5, lon == 165.5, !is.na(cant_total)) %>%
        arrange(depth),
      aes(cant_total, depth, col = "mapped")
    ) +
    geom_point(
      data = GLODAP_cant_obs %>%
        filter(lat == 48.5, lon == 165.5, !is.na(cant_total)) %>%
        arrange(depth),
      aes(cant_total, depth, col = "mapped")
    ) +
    geom_point(
      data = GLODAP_cant_obs %>%
        filter(lat == 48.5, lon == 165.5, month == 6),
      aes(cant_int, depth, col = "interpolated")
    ) +
    scale_y_reverse() +
    facet_wrap( ~ era) +
    scale_color_brewer(palette = "Dark2", name = "") +
    labs(title = "Cant interpolation to subsetting depth - example profile")
  
}

# remove cant data at grid cells without observations
GLODAP <- GLODAP_cant_obs %>%
  filter(!is.na(cstar)) %>%
  mutate(cant_total_pos = cant_int) %>%
  select(-c(cant_int, cant_total, n))

rm(GLODAP_cant_obs)

```


### Merge GLODAP + atm. pCO~2~

GLODAP-based subsetting were merged with mean annual atmospheric pCO~2~ levels by year.

```{r merge_cstar_pCO2}

GLODAP <- left_join(GLODAP, co2_atm)

```

### Calculation

```{r adjust_reference_year}

# assign reference year
GLODAP <- GLODAP %>% 
  group_by(era) %>% 
  mutate(tref = median(year)) %>% 
  ungroup()

# extract atm pCO2 at reference year
co2_atm_tref <- right_join(co2_atm, tref) %>% 
  select(-year) %>% 
  rename(pCO2_tref = pCO2)

# merge atm pCO2 at tref with GLODAP
GLODAP <- full_join(GLODAP, co2_atm_tref)
rm(co2_atm, tref)

# calculate cstar for reference year
GLODAP <- GLODAP %>%
  mutate(
    cstar_tref_delta =
      ((pCO2 - pCO2_tref) / (pCO2_tref - params_local$preind_atm_pCO2)) * cant_total_pos,
    cstar_tref = cstar - cstar_tref_delta)

```


## Control plots

```{r cstar_reference_year_adjustment_histogram}

GLODAP %>% 
  ggplot(aes(cstar_tref_delta)) +
  geom_histogram(binwidth = 1) +
  labs(title = "Histogramm with binwidth = 1")

```

```{r cstar_reference_year_adjustment_vs_time_cant}

GLODAP %>% 
  sample_n(1e4) %>% 
  ggplot(aes(year, cstar_tref_delta, col = cant_total_pos)) +
  geom_point() +
  scale_color_viridis_c() +
  labs(title = "Time series of random subsample 1e4")

```

```{r cstar_reference_year_adjustment_vs_time_counts}

GLODAP %>% 
  ggplot(aes(year, cstar_tref_delta)) +
  geom_bin2d(binwidth = 1) +
  scale_fill_viridis_c(trans = "log10") +
  labs(title = "Heatmap with binwidth = 1")

```

# Selected section plots

A selected section is plotted to demonstrate the magnitude of various parameters and corrections relevant to C*.

```{r select_cruises}

if (params_local$subsetting == "GLODAP") {

GLODAP_cruise <- GLODAP %>% 
  filter(cruise %in% params_global$cruises_meridional)

}

if (params_local$subsetting == "random") {
  
  GLODAP_cruise <- GLODAP %>%
    filter(lon %in% params_global$lon_Atl_section)
  
}

```


```{r meridional_sections, fig.asp=0.5}

if (params_local$subsetting == "GLODAP") {
  map +
    geom_path(data = GLODAP_cruise %>%
                arrange(date),
              aes(lon, lat)) +
    geom_point(data = GLODAP_cruise %>%
                 arrange(date),
               aes(lon, lat, col = date)) +
    scale_color_viridis_c(trans = "date") +
    labs(title = paste("Cruise year:", mean(GLODAP_cruise$year)))
}

if (params_local$subsetting == "random") {
  map +
    geom_path(data = GLODAP_cruise,
              aes(lon, lat)) +
    geom_point(data = GLODAP_cruise,
               aes(lon, lat)) +
    scale_color_viridis_c(trans = "date") +
    labs(title = paste("Cruise year:", mean(GLODAP_cruise$year)))
  
}

lat_section <-
  GLODAP_cruise %>%
  ggplot(aes(lat, depth)) +
  scale_y_reverse() +
  scale_fill_viridis_c() +
  theme(axis.title.x = element_blank())

for (i_var in c("tco2",
                "rCP_phosphate",
                "talk_05",
                "rNP_phosphate_05",
                "cstar",
                "cstar_tref")) {
  print(lat_section +
          stat_summary_2d(aes(z = !!sym(i_var))) +
          scale_fill_viridis_c(name = i_var)
        )
  
}

rm(lat_section, GLODAP_cruise)

```


# Isoneutral slabs

The following boundaries for isoneutral slabs were defined:

- Atlantic: `r params_local$slabs_Atl`
- Indo-Pacific: `r params_local$slabs_Ind_Pac`

Continuous neutral densities (gamma) values from model subsetting are grouped into isoneutral slabs.

```{r cut_isoneutral_slabs}

GLODAP <- m_cut_gamma(GLODAP, "gamma")

```

```{r meridional_sections_isoneutral_slabs, fig.asp=0.6}

if (params_local$subsetting == "GLODAP") {

GLODAP_cruise <- GLODAP %>% 
  filter(cruise %in% params_global$cruises_meridional)

}

if (params_local$subsetting == "random") {
  
  GLODAP_cruise <- GLODAP %>% 
  filter(lon %in% params_global$lon_Atl_section)
  
}

lat_section <- 
GLODAP_cruise %>%
  ggplot(aes(lat, depth)) +
  scale_y_reverse() +
  theme(legend.position = "bottom")

lat_section +
  geom_point(aes(col = gamma_slab)) +
  scale_color_viridis_d()

rm(lat_section, GLODAP_cruise)

```


```{r test_isoneutral_density_calculation, eval=FALSE, hide=TRUE}

# this section was only used to calculate gamma locally, and compare it to the value provided in GLODAP data set
if (params_local$subsetting == "GLODAP") {

GLODAP_cruise <- GLODAP %>% 
  filter(cruise %in% params_global$cruises_meridional)

}

if (params_local$subsetting == "random") {
  
  GLODAP_cruise <- GLODAP %>% 
  filter(lon %in% params_global$lon_Atl_section)
  
}

library(oce)
library(gsw)
# calculate pressure from depth

GLODAP_cruise <- GLODAP_cruise %>% 
  mutate(CTDPRS = gsw_p_from_z(-depth,
                               lat))

GLODAP_cruise <- GLODAP_cruise %>% 
  mutate(THETA = swTheta(salinity = sal,
                         temperature = temp,
                         pressure = CTDPRS,
                         referencePressure = 0,
                         longitude = lon-180,
                         latitude = lat))

GLODAP_cruise <- GLODAP_cruise %>% 
  rename(LATITUDE = lat,
         LONGITUDE = lon,
         SALNTY = sal,
         gamma_provided = gamma)

library(reticulate)
source_python(
  paste(
    path_root,
    "/utilities/functions/python_scripts/",
    "Gamma_GLODAP_python.py",
    sep = ""
  )
)

GLODAP_cruise <- calculate_gamma(GLODAP_cruise)

GLODAP_cruise <- GLODAP_cruise %>% 
  mutate(gamma_delta = gamma_provided - GAMMA)

lat_section <- 
GLODAP_cruise %>%
  ggplot(aes(LATITUDE, CTDPRS)) +
  scale_y_reverse() +
  theme(legend.position = "bottom")

lat_section +
  stat_summary_2d(aes(z = gamma_delta)) +
  scale_color_viridis_c()

GLODAP_cruise %>% 
  ggplot(aes(gamma_delta))+
  geom_histogram()

rm(lat_section, GLODAP_cruise, cruises_meridional)

```


# Synthetic data coverage

```{r obs_gamma_slab, fig.asp=1}

GLODAP <- GLODAP %>% 
  mutate(gamma_slab = factor(gamma_slab), 
         gamma_slab = factor(gamma_slab, levels = rev(levels(gamma_slab))))

for (i_basin in unique(GLODAP$basin)) {
  # i_basin <- unique(GLODAP$basin)[3]
  
  print(
    GLODAP %>%
      filter(basin == i_basin) %>%
      ggplot(aes(lat, gamma_slab)) +
      geom_bin2d(binwidth = 5) +
      scale_fill_viridis_c(
        option = "magma",
        direction = -1,
        trans = "log10"
      ) +
      scale_x_continuous(breaks = seq(-100, 100, 20),
                         limits = c(params_global$lat_min,
                                    params_global$lat_max)) +
      facet_grid(era ~ .) +
      labs(title = paste("MLR region: ", i_basin))
  )
  
}

```


## Histograms

```{r histogram_predictor, fig.asp=1}

GLODAP_vars <- GLODAP %>% 
  select(params_local$MLR_target,
         params_local$MLR_predictors)

GLODAP_vars_long <- GLODAP_vars %>% 
  pivot_longer(
    cols = c(params_local$MLR_target,
             params_local$MLR_predictors),
    names_to = "variable",
    values_to = "value"
  )

GLODAP_vars_long %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~ variable,
             ncol = 2,
             scales = "free")

rm(GLODAP_vars, GLODAP_vars_long)

```


# Individual cruise sections

Zonal and meridional section plots are produce for each cruise individually and are available under:  

`r paste(path_version_figures, "Cruise_sections_histograms/", sep = "")`

```{r plot_all_individual_cruises_clean, eval=FALSE}

if (params_local$subsetting == "GLODAP") {
  if (params_local$plot_all_figures == "y") {
    cruises <- GLODAP %>%
      group_by(cruise) %>%
      summarise(date_mean = mean(date, na.rm = TRUE),
                n = n()) %>%
      ungroup() %>%
      arrange(date_mean)
    
    GLODAP <- full_join(GLODAP, cruises)
    
    n <- 0
    for (i_cruise in unique(cruises$cruise)) {
      # i_cruise <- unique(cruises$cruise)[1]
      # n <- n + 1
      # print(n)
      
      GLODAP_cruise <- GLODAP %>%
        filter(cruise == i_cruise) %>%
        arrange(date)
      
      cruises_cruise <- cruises %>%
        filter(cruise == i_cruise)
      
      map_plot <-
        map +
        geom_point(data = GLODAP_cruise,
                   aes(lon, lat, col = date)) +
        scale_color_viridis_c(trans = "date") +
        labs(
          title = paste(
            "Mean date:",
            cruises_cruise$date_mean,
            "| cruise:",
            cruises_cruise$cruise,
            "| n(samples):",
            cruises_cruise$n
          )
        )
      
      
      lon_section <- GLODAP_cruise %>%
        ggplot(aes(lon, depth)) +
        scale_y_reverse() +
        scale_fill_viridis_c()
      
      lon_tco2 <- lon_section +
        stat_summary_2d(aes(z = tco2))
      
      lon_talk <- lon_section +
        stat_summary_2d(aes(z = talk))
      
      lon_phosphate <- lon_section +
        stat_summary_2d(aes(z = phosphate))
      
      lon_oxygen <- lon_section +
        stat_summary_2d(aes(z = oxygen))
      
      lon_aou <- lon_section +
        stat_summary_2d(aes(z = aou))
      
      lon_phosphate_star <- lon_section +
        stat_summary_2d(aes(z = phosphate_star))
      
      lon_nitrate <- lon_section +
        stat_summary_2d(aes(z = nitrate))
      
      lon_cstar <- lon_section +
        stat_summary_2d(aes(z = cstar_tref))
      
      
      lat_section <- GLODAP_cruise %>%
        ggplot(aes(lat, depth)) +
        scale_y_reverse() +
        scale_fill_viridis_c()
      
      lat_tco2 <- lat_section +
        stat_summary_2d(aes(z = tco2))
      
      lat_talk <- lat_section +
        stat_summary_2d(aes(z = talk))
      
      lat_phosphate <- lat_section +
        stat_summary_2d(aes(z = phosphate))
      
      lat_oxygen <- lat_section +
        stat_summary_2d(aes(z = oxygen))
      
      lat_aou <- lat_section +
        stat_summary_2d(aes(z = aou))
      
      lat_phosphate_star <- lat_section +
        stat_summary_2d(aes(z = phosphate_star))
      
      lat_nitrate <- lat_section +
        stat_summary_2d(aes(z = nitrate))
      
      lat_cstar <- lat_section +
        stat_summary_2d(aes(z = cstar_tref))
      
      
      hist_tco2 <- GLODAP_cruise %>%
        ggplot(aes(tco2)) +
        geom_histogram()
      
      hist_talk <- GLODAP_cruise %>%
        ggplot(aes(talk)) +
        geom_histogram()
      
      hist_phosphate <- GLODAP_cruise %>%
        ggplot(aes(phosphate)) +
        geom_histogram()
      
      hist_oxygen <- GLODAP_cruise %>%
        ggplot(aes(oxygen)) +
        geom_histogram()
      
      hist_aou <- GLODAP_cruise %>%
        ggplot(aes(aou)) +
        geom_histogram()
      
      hist_phosphate_star <- GLODAP_cruise %>%
        ggplot(aes(phosphate_star)) +
        geom_histogram()
      
      hist_nitrate <- GLODAP_cruise %>%
        ggplot(aes(nitrate)) +
        geom_histogram()
      
      hist_cstar <- GLODAP_cruise %>%
        ggplot(aes(cstar_tref)) +
        geom_histogram()
      
      (map_plot /
          ((hist_tco2 / hist_talk / hist_phosphate / hist_cstar) |
             (
               hist_oxygen / hist_phosphate_star / hist_nitrate / hist_aou
             )
          )) |
        ((
          lat_tco2 / lat_talk / lat_phosphate / lat_oxygen / lat_aou / lat_phosphate_star / lat_nitrate / lat_cstar
        ) |
          (
            lon_tco2 / lon_talk / lon_phosphate / lon_oxygen /  lon_aou / lon_phosphate_star / lon_nitrate / lon_cstar
          )
        )
      
      ggsave(
        path = paste(
          path_version_figures,
          "Cruise_sections_histograms/",
          sep = ""
        ),
        filename = paste(
          "Cruise_date",
          cruises_cruise$date_mean,
          "count",
          cruises_cruise$n,
          "cruiseID",
          cruises_cruise$cruise,
          ".png",
          sep = "_"
        ),
        width = 20,
        height = 12
      )
      
      rm(
        map_plot,
        lon_section,
        lat_section,
        lat_tco2,
        lat_talk,
        lat_phosphate,
        lon_tco2,
        lon_talk,
        lon_phosphate,
        GLODAP_cruise,
        cruises_cruise
      )
      
    }
    
  }
  
}

```


# Write files

```{r write_csv_GLODAP_used_for_fitting}

if (params_local$subsetting == "GLODAP") {
  # select relevant columns
  GLODAP <- GLODAP %>%
    select(
      year,
      date,
      era,
      basin,
      basin_AIP,
      lat,
      lon,
      depth,
      gamma,
      gamma_slab,
      params_local$MLR_predictors,
      params_local$MLR_target
    )
  
  GLODAP %>% write_csv(paste(
    path_version_data,
    "GLODAPv2.2020_MLR_fitting_ready.csv",
    sep = ""
  ))
  
}

if (params_local$subsetting == "random") {
  # select relevant columns
  GLODAP <- GLODAP %>%
    select(
      year,
      month,
      era,
      basin,
      basin_AIP,
      lat,
      lon,
      depth,
      gamma,
      gamma_slab,
      params_local$MLR_predictors,
      params_local$MLR_target
    )
  
  GLODAP %>% write_csv(paste(
    path_version_data,
    "GLODAPv2.2020_MLR_fitting_ready.csv",
    sep = ""
  ))
}

co2_atm_tref %>%  write_csv(paste(path_version_data,
                                  "co2_atm_tref.csv",
                                  sep = ""))

```
